A Polls-of-Polls Forecast for the 2024 United States Presidential Election:Analysis of Support for Harris Factoring Pollster Differences

### 2024-11-03 paper/paper.qmd
update on used libraries and references

library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(knitr)
library(rstanarm)
library(modelsummary)

@@

In performing the analysis, we used several R pacakages. We used tidyverse [@tidyverse] for data manipulation and visualization, and rstanarm [@rstanarm] for Bayesian modeling. We also used modelsummary [@modelsummary] to generate model summaries.To visualize results, we used ggplot2 [@ggplot2] and kable [@kable] *ADD KABLE CITATION?* to format tables for presentation.

>>>>

library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(knitr)
library(rstanarm)

@@

In performing the analysis, we used several R pacakages. We used tidyverse [@tidyverse] for data manipulation and visualization, and rstanarm [@rstanarm] for Bayesian modeling. To visualize results, we used ggplot2 [@ggplot2] and kableExtra [@citekableExtra] to format tables for presentation.
